Gametic Selection, Meiotic Drive, Sex Ratio Bias, and Transitions Between sex-determination systems

### 2017-07-06 LaTeX/Turnover.tex
comment that we can only do ESD for weak sel

We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determiner, ESD). 
We assume that individuals carrying the $m$ allele develop as females with probability $k$ (e.g., in a fraction $k$ of the environments they randomly experience). 
Assuming weak selection, the spread of these mutations is given by

>>>>

\textcolor{blue}{The characteristic polynomial describing eigenvalues of the 8 equation system (describing growth rate on XA, Xa, YA, Ya backgrounds in males and females) does not reduce for ESD mutants as it does for $k=0$ or $k=1$. Therefore we focus on weak selection here.}
We next consider the case where the new sex-determining mutation, $m$, causes sex to be determined probabilistically or by heterogeneous environmental conditions (environmental sex determiner, ESD). 
We assume that individuals carrying the $m$ allele develop as females with probability $k$ (e.g., in a fraction $k$ of the environments they randomly experience). 
Assuming weak selection, the spread of these mutations is given by
